Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/linear-density-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by each tesseroid shell model
    and the analytical solution.
    Each model has a linear density function (Eq.~\ref{eq:density-linear}).
    The computations were performed on the four grids described in Table~\ref{tab:grids}
    and using the shell models detailed in Table~\ref{tab:shell-models}.
    Each line represents the maximum absolute difference between every shell model.
    Due to the linearity of the density function, the density-based discretization
    algorithm is not applied.
    Differences are reported as a percentage of the shell values.
    The horizontal dashed black line represents a target difference of 0.1\%.
}
\label{fig:D-linear}
\end{figure*}

@@

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/exponential-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/exponential-densities.pdf}
}
\caption{
    Exponential density functions assigned to each spherical shell in the $D$ and
    $\delta$ ratios determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-exp}.
}
\label{fig:exp-densities}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/exponential-density-diffs.pdf}
\caption{
    Numerical error for different exponential density functions and values of the delta
    ratio.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by the spherical shell with an exponential density function and
    different values of $b$ (Eq.~\ref{eq:density-exp}).
    These comparisons were carried out on every grid defined on Table~\ref{tab:grids},
    making use of the shell models detailed on Table~\ref{tab:shell-models} and
    fixing the distance-size ratio $D$ to the values obtained for the linear density
    case.
    Each curve corresponds to the maximum difference between every shell model with the
    same value of $b$.
    }
\label{fig:delta-exponential}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/sine-density-diffs.pdf}
\caption{
    Numerical error for different sinusoidal density functions and values of the delta
    ratio.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by the spherical shell with an exponential density function and
    different values of $b$ (Eq.~\ref{eq:density-sine}).
    These comparisons were carried out on every grid defined on Table~\ref{tab:grids},
    making use of the shell models detailed on Table~\ref{tab:shell-models} and
    fixing the distance-size ratio $D$ to the values obtained for the linear density
    case.
    Each curve corresponds to the maximum difference between every shell model with the
    same value of $b$.
    }
\label{fig:delta-sine}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/linear-density-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by each tesseroid shell model
    and the analytical solution as a function of the distance-size ratio $D$.
    Each model has a linear density function (Eq.~\ref{eq:density-linear}).
    The computations were performed on the four grids described in Table~\ref{tab:grids}
    and using the shell models detailed in Table~\ref{tab:shell-models}.
    Each line represents the maximum absolute difference between the numerical results
    and the analytical solution for a given shell model.
    Due to the linearity of the density function, the density-based discretization
    algorithm is not applied.
    Differences are reported as a percentage of the analytical solutions.
    The horizontal dashed black line represents a target difference of 0.1\%.
}
\label{fig:D-linear}
\end{figure*}

@@

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/exponential-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/exponential-densities.pdf}
}
\caption{
    Exponential density functions assigned to the spherical shell models for
    $\delta$ ratio determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-exp}.
}
\label{fig:exp-densities}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/exponential-density-diffs.pdf}
\caption{
    Difference between the numerical and analytical solutions as a function of $\delta$
    ratio for different exponential density functions.
    These comparisons were carried out for every shell model
    (Table~\ref{tab:shell-models}) and computation grid (Table~\ref{tab:grids})
    using a fixed value of $D$.
    Each curve corresponds to the maximum difference out of all shell models
    for a particular value of $b$ (Eq.~\ref{eq:density-exp}).
    Differences are reported as a percentage of the analytical solutions.
    The horizontal dashed black line represents a target difference of 0.1\%.
    }
\label{fig:delta-exponential}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/sine-density-diffs.pdf}
\caption{
    Difference between the numerical and analytical solutions as a function of $\delta$
    ratio for different sinusoidal density functions.
    These comparisons were carried out for every shell model
    (Table~\ref{tab:shell-models}) and computation grid (Table~\ref{tab:grids})
    using a fixed value of $D$.
    Each curve corresponds to the maximum difference out of all shell models
    for a particular value of $b$ (Eq.~\ref{eq:density-sine}).
    Differences are reported as a percentage of the analytical solutions.
    The horizontal dashed black line represents a target difference of 0.1\%.
    }
\label{fig:delta-sine}
\end{figure*}
